Mass and occupation fraction of dark matter halos hosting Lyman-$\alpha$ emitters at $z\sim 3$

### 2014-01-20 paper/ms.tex
revised abstract

\title[Halo mass and occupation fraction of LAEs at$z=3.1$]{Mass and
  occupation fraction of dark matter halos hosting Lyman-$\alpha$
  emitters at $z\sim 3$}      
\author[~J.~E. Forero-Romero and ~J.~E. Mejia-Restrepo]{
\parbox[t]{\textwidth}{\raggedright 
  Jaime E. Forero-Romero$^{1}$ and
  Julian E. Mej\'ia-Restrepo$^{2,3}$ 
}
\vspace*{6pt}\\
$^{1}$ Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
No. 18A-10, Edificio Ip, Bogot\'a, Colombia \\
$^{2}$ Departamento de Astronom\'{i}a, Universidad de Chile, Camino el
Observatorio 1515, Santiago, Chile\\
$^3$FACom-Instituto de Física-FCEN, Universidad de Antioquia, Calle 70 No. 52-21, Medellín, Colombia}

@@

\begin{abstract}
%
We derive constraints on the mass and occupation fraction of dark
matter halos hosting \ly Emitting galaxies (LAEs) at a redshift of
$z=3.1$ by matching the number density distribution and the angular
correlation function between mock and observed fields. We explicitly
take into account the cosmic variance on the typical observed field
size by constructing mock fields from a large cosmological N-body
simulation with the same geometry of observed fields. To populate the
halos in the simulation we use a model where a dark matter halo with
mass in the range $M_{\rm min}<M_{\rm h}<M_{\rm max}$ can only host
one detectable LAE with a probability $0.1 \leq f_{\rm occ}\leq
1.0$. We avoid the large uncertainties in the estimation of \ly
luminosities with this approach. Our main result is that the
clustering and number density information are insufficient to impose a
tight constraint on the {\bf   occupation} fraction. On the other hand
the minimum mass and maximum mass can be constrained to the range $M_{\rm max}<10^{12}$\hMsun and $10^{10}\hMsun\leq M_{\rm min}\leq
10^{11.5}\hMsun$.  We also find that the consistent models have a narrow mass
range, $\Delta M \equiv \log_{10}M_{\rm max} - \log_{10} M_{\rm min}$,
smaller than $1.0$ dex, with a vast majority in the range $\Delta
M<0.5$ dex. {\bf These mass ranges are a sub-set of already published
constraints, while the wide range of values for the escape fraction
  are a novel result}. There is an inconclusive response as to
which is the occupation fraction for LAEs at $z=3.1$. A precise answer
requires observations on larger fields and robust physical models for
the connection between dark matter, star formation and the escape of
\ly radiation. That kind of modeling should also be able to provide a
plausible explanation for the narrow range in mass $\Delta M<1.0$ dex
derived here for the halos hosting LAEs at $z=3.1$.

\end{abstract}

>>>>

\title[Halo mass and occupation fraction of LAEs at$z=3.1$]{Mass and
  occupation fraction of dark matter halos hosting Lyman-$\alpha$
  emitters at $z\sim 3$}      
\author[~J.~E. Forero-Romero and ~J.~E. Mejia-Restrepo]{
\parbox[t]{\textwidth}{\raggedright 
  Jaime E. Forero-Romero$^{1}$ and
  Julian E. Mej\'ia-Restrepo$^{2,3}$ 
}
\vspace*{6pt}\\
$^{1}$ Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
No. 18A-10, Edificio Ip, Bogot\'a, Colombia \\
$^{2}$ Departamento de Astronom\'{i}a, Universidad de Chile, Camino el
Observatorio 1515, Santiago, Chile\\
$^3$ FACom-Instituto de F\'isica-FCEN, Universidad de Antioquia, Calle 70 No. 52-21, Medell\'in, Colombia}

@@

\begin{abstract}
%
We derive constraints on the mass and occupation fraction of dark
matter halos hosting \ly Emitting galaxies (LAEs) at a redshift of
$z=3.1$ by matching the number density distribution and the angular
correlation function between mock and observed fields. We explicitly
take into account the cosmic variance on the typical observed field
size by constructing mock fields from a large cosmological N-body
simulation. To populate the
halos in the simulation we use a model where a dark matter halo with
mass in the range $M_{\rm min}<M_{\rm h}<M_{\rm max}$ can only host
one detectable LAE with a probability $0.1 \leq f_{\rm occ}\leq
1.0$. {\bf We use this approach to avoid the uncertainties associated
  to the estimation of \ly luminosities in each halo.} Our analysis
shows that the clustering and number density information are
insufficient to impose a tight constraint on the {\bf   occupation}
fraction. On the other hand, the minimum mass and maximum mass can be
constrained to the range $M_{\rm  max}<10^{12}$\hMsun and
$10^{10.2}\hMsun\leq M_{\rm min}\leq 10^{11.5}\hMsun$.  We also find
that the consistent models have a narrow mass range, $\Delta M \equiv
\log_{10}M_{\rm max} - \log_{10} M_{\rm min}$, smaller than $1.0$ dex,
with a majority in the range $\Delta M<0.5$ dex. {\bf These results
  broadly reproduce some constraints   already presented in the
  literature. However, the wide range of  values for the escape
  fraction and the narrow mass ranges are novel results from
  the approach presented here}. We conclude that achieving a constraint on the
occupation fraction for LAEs at $z=3.1$ will require observations on
larger fields to reduced cosmic variance and robust physical models
for the connection between dark matter, star formation and the escape
of \ly radiation. That kind of modeling should also be able to provide
a plausible explanation for the narrow mass range derived here for the
halos hosting LAEs at $z=3.1$. 
\end{abstract}
